Flare Rates and Rotation Periods of 5700 Stars Younger than 300 Myr

### 2023-11-07 src/tex/ms.tex
galex subsection

\begin{figure*}[ht!]
    \script{mcmc_results.py}
    \begin{centering}
        \includegraphics[width=3\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
        \caption{
            Measured flare-frequency distribution slopes, $\alpha$, as a function
            of stellar effective temperature, $T_\textrm{eff}$ and age.
        }
        \label{fig:mcmc_results}
    \end{centering}
\end{figure*}

@@

@@

\subsection{Correlation to Other Metrics of Magnetic Saturation}

Here, we explore if flare rates evolve as a function of rotation period. We used our
measured $P_\textrm{rot}$ as described in Section~\ref{subsec:prot}. Due to TESS's orbit,
we limit our search of $P_\textrm{rot}$ to $< 20$\,days. This should not bias our analysis as
young stars are known to rotate on short timescales \citep[e.g.][]{west15, popinchalk23}. We
present our results in Figure~\ref{fig:prot}.

>>>>

\begin{figure*}[ht!]
    \script{mcmc_results.py}
    \begin{centering}
        \includegraphics[width=3.4\textwidth, trim={0 0 30mm 0}, clip]{figures/mcmc_results.pdf}
        \caption{
            Measured flare-frequency distribution slopes, $\alpha$, as a function
            of stellar effective temperature, $T_\textrm{eff}$ and age.
        }
        \label{fig:mcmc_results}
    \end{centering}
\end{figure*}

@@

\subsection{Correlations with Far- and Near-Ultraviolet Flux}

The Far- and Near-Ultraviolet (FUV/NUV) is another tracer of magnetic activity. Young
stars are known to have excess luminosity in both of these wavelengths \citep{}. We use
archival observations from the \textit{Galaxy Evolution Explorer}
\citep[\textit{GALEX};][]{martin05} to search for trends in FUV/NUV saturation and flare
rate saturation. \textit{GALEX} provides broad FUV photometry from $1350-1750$
and NUV photometry from $1750-2750$. We crossmatch our targets with the \textit{GALEX}
catalog. We follow the sample selection methods outline in \citep{schneider18}. We search
a $10''$ radius around the coordinates of each target in our sample. We include targets with
no bad photometric flags (e.g. \texttt{fuv\_artifact} or \texttt{nuv\_artifact == 0}) as defined
in the catalog. This is recommended by the \textit{GALEX} documentation, as flags could be
assigned due to bright star window reflection, dichroic reflection, detector run proximity,
or bright star ghost. We exclude targets with measured magnitudes brighter than 15, which
marks the saturation limit for both the FUV and NUV photometers \citep{morrissey07}.

Based on these thresholds, we find that 462 stars in our sample have NUV photometry and
139 stars have FUV photometry. We explore if flare rate saturation and FUV/NUV saturation
are correlated with the derived $R_0$ per star. We present our results in Figure~\ref{fig:galex}.
We present the measured FUV/NUV flux normalized by the J-band flux of the star, since it
is the fractional flux which acts as an activity indicator. While bolometric luminosities would
be a better normalizing factor, we find the majority of stars in our target do not have
this parameter measured. To assess FUV/NUV correlations in a larger statistical sense, we thus
keep the normalization to $f_J$.

\begin{figure}[ht!]
    \script{galex.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/galex.pdf}
        \caption{
            Calculated NUV (left) and FUV (right) GALEX flux for stars in our
            sample. We normalize these values by the J-band flux of the star.
            We find no strong correlation between the NUV/FUV flux and the measured
            flare rate or Rossby number.
            The top row shows GKM stars $<50$~Myr; the bottom row
            shows GKM stars $\geq 50$~Myr. M stars are shown as circles, K stars as
            triangles, and G stars as squares. We note that $f_{NUV}$ traces the
            photosphere of GK stars, and therefore may not be the best comparison
            bandpass when looking for trends in magnetic activity.
        }
        \label{fig:galex}
    \end{centering}
\end{figure}

@@
